Kindly Bent to Free Us

### 2019-09-20 kindly/popl20-rebuttal.md

We thank the reviewers for their thoughtful comments.
We will take their comments into account and revise our article as follows.
* Streamline the description of examples in Section 2 to focus on Affe's novelties
* Present automatic region annotation in the body of the article and clarify its role in the type system.
* Present the pattern matching rules, both typing and semantic.
* Improve the explanation through new examples for the semantics and
  the type inference.

@@

# Reviewer D

## Partial inference and GADT

Even if a language does not admit full type inference, we believe
there should be a well-defined core language which does.
This way, a programmer who steps over the boundary knows when type
annotations are needed.
In particular, it is possible (and desirable) to extend Affe with existential types
by requiring type annotations, similarly to Alms.
The results we present nevertheless garantee that
full type inference is supported in the absence of existentials.

## Examples

We strongly believe programming examples are essential to demonstrate and explain
Affe's features, as highlighted in reviewer C's answer. We do agree that semantics and inference require more examples, one of which is already available in Appendix B.1.
